Inference of Gravitational Lens Time Delays Using Gaussian Processes

### 2012-05-30 doc/ms.tex
No figures - paper now compiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\includegraphics[scale=0.75]{figs1/b1608_data.eps}
\caption{Monitoring data for B1608+656.\label{b1608_data}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\includegraphics{figs1/b1608_delays.eps}
\caption{Inferred time delays for B1608+656.\label{b1608_delays}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[scale=0.42]{figs1/correlation.eps}
\caption{Inferred intrinsic QSO variability parameters for B1608+656. This is the only significant correlation in the joint posterior distribution. The data are consistent with a small or large value for the variability amplitude, but if the amplitude is large, then the timescale must also be large so that we have only observed a small portion of the timescale.\label{correlation}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}
%\includegraphics[scale=0.75]{figs1/b1608_data.eps}
%\caption{Monitoring data for B1608+656.\label{b1608_data}}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}
%\includegraphics{figs1/b1608_delays.eps}
%\caption{Inferred time delays for B1608+656.\label{b1608_delays}}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}
%\includegraphics[scale=0.42]{figs1/correlation.eps}
%\caption{Inferred intrinsic QSO variability parameters for B1608+656. This is the only significant correlation in the joint posterior distribution. The data are consistent with a small or large value for the variability amplitude, but if the amplitude is large, then the timescale must also be large so that we have only observed a small portion of the timescale.\label{correlation}}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
